---
title: "youtube"
author: "StephanLewandowsky"
date: "2019-12-31"
output: 
   workflowr::wflow_html:
     code_folding: hide
     number_sections: yes
     toc: yes
     toc_depth: 3
     toc_float: yes
     theme: cosmo
     highlight: textmate
editor_options:
  chunk_output_type: console
---

## Introduction

```{r echo=TRUE, warning=FALSE, message=FALSE, results="hide"}
rm(list=ls())
library(lattice)
library(ggplot2)
library(tabplot)
library(tidyverse)
library(lme4)
library(RColorBrewer)
library(gridExtra)
library(stringr)
library(Hmisc)
library(reshape2)
library(psych)
library(scales)
library(summarytools) #contains descr()
library(foreign) #for SPSS
library(workflowr)
library(olsrr)
library(corrplot)
library(vioplot)

#define working directories
inputdir <- "data"

iphob <- read.spss(paste(inputdir,"IslamophobiaSPSSDATA.sav",sep="/"), use.value.labels = TRUE, to.data.frame = TRUE)
irad <-  read.spss(paste(inputdir,"RadicalisationSPSS.sav",sep="/"), use.value.labels = TRUE, to.data.frame = TRUE)
irad <- irad[!rowSums(is.na(irad))==dim(irad)[2], ]
```

## Summary statistics for Islamophobia
```{r summary, echo=TRUE, warning=FALSE, message=FALSE}
descr(iphob)
tableplot(iphob)

temp1 <- iphob %>% select(c(Modularity,MisinformationPerMinute,BetweennessCentrality,
                            Views,VideoLength,LikestoDislikes,LikesPerView,DislikesPerView,
                            AdConsequentiam, AdHomien, AdPopulum, FalseCause, HastyGeneralisations,
                            Polarisation, InvokingEmotion, Conspiracy, Trolling, DeflectingBlame,
                            MisrepresentationScripture, CherryPickedData)) 
#zero likes is a clear outlier after log transform, so remove it
temp1$LikesPerView[temp1$LikesPerView==0]<-NA
temp1$LikestoDislikes[temp1$LikestoDislikes==0]<-NA
temp1$sumallrhetoric <- temp1 %>% select(AdConsequentiam:CherryPickedData) %>% apply(.,1,sum)

iphomainvars <- data.frame(temp1,
                           temp1 %>% select(c(MisinformationPerMinute, BetweennessCentrality, Views,
                                              VideoLength, LikestoDislikes ,LikesPerView, DislikesPerView, sumallrhetoric)) %>% 
                                     mutate_all(~ log(. + .0001)) %>%
                                     rename_all( ~paste0(., "_log") ))
multi.hist(iphomainvars%>%select(contains("log")))


#corrplot...
RM  <- cor(iphomainvars%>%select(contains("log")))
RM2 <- cor.mtest(iphomainvars%>%select(contains("log")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
#colnames(RM) <- rownames(RM) <- c("Conservatism","Truth Knowable","Intuitive","Conspiracism","Need for Chaos","Knowledge Source",
#"Consensus AIDS","Consensus Vaccinations","Consensus Climate")
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)
#dev.print(pdf,paste(figdir,"cormat.pdf",sep="/"))


```
## Predict various outcomes for Islamophobia

### Predict views for Islamophobia
```{r regphobviews, echo=TRUE, warning=FALSE, message=FALSE}

indepvars <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-Views_log)),collapse=" + ")

allregFormula <- as.formula(paste("Views_log ~ ",indepvars))
viewmod <- lm(allregFormula, data=iphomainvars)
allregs <- ols_step_all_possible(viewmod)
plot(allregs)

topmodels <- allregs[order(allregs$n,-allregs$rsquare) , ]
topmodels[!duplicated(topmodels$n),]

#summarize the 'best' model (3 predictors, model 29)
indepvars2 <- paste(unlist(str_split(allregs[1,]$predictors," ")),collapse=" + ")
bmFormula <- as.formula(paste("Views_log ~ ", indepvars2))
viewbestmod <- lm(bmFormula, data=iphomainvars)
summary(viewbestmod)

```

### Predict centrality for Islamophobia
```{r regphobcent, echo=TRUE, warning=FALSE, message=FALSE}

indepvars3 <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-BetweennessCentrality_log)),collapse=" + ")

allregFormula2 <- as.formula(paste("BetweennessCentrality_log ~ ",indepvars3))
centmod <- lm(allregFormula2, data=iphomainvars)
allregs2 <- ols_step_all_possible(centmod)
plot(allregs2)

topmodels2 <- allregs2[order(allregs2$n,-allregs2$rsquare) , ]
topmodels2[!duplicated(topmodels2$n),]

#summarize the 'best' model
indepvars4 <- paste(unlist(str_split(allregs2[29,]$predictors," ")),collapse=" + ")
bmFormula2 <- as.formula(paste("BetweennessCentrality_log ~ ", indepvars4))
centbestmod <- lm(bmFormula2, data=iphomainvars)
summary(centbestmod)

```

### Predict likes to dislikes for Islamophobia
```{r regphobl2d, echo=TRUE, warning=FALSE, message=FALSE}

indepvars5 <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:VideoLength_log,sumallrhetoric_log))),collapse=" + ")

allregFormula3 <- as.formula(paste("LikestoDislikes_log ~ ",indepvars5))
l2dmod <- lm(allregFormula3, data=iphomainvars)
allregs3 <- ols_step_all_possible(l2dmod)
plot(allregs3)

topmodels3 <- allregs3[order(allregs3$n,-allregs3$rsquare) , ]
topmodels3[!duplicated(topmodels3$n),]

#summarize the 'best' model
indepvars6 <- paste(unlist(str_split(allregs3[1,]$predictors," ")),collapse=" + ")
bmFormula3 <- as.formula(paste("LikestoDislikes_log ~ ", indepvars6))
l2dbestmod <- lm(bmFormula3, data=iphomainvars)
summary(l2dbestmod)

```


## Summary statistics for Radical Islamist
```{r radsummary, echo=TRUE, warning=FALSE, message=FALSE}
descr(irad)
tableplot(irad)

temp1 <- irad %>% select(c(Modularity,MisinformationPerMinute,BetweennessCentrality,
                            Views,VideoLength,LikesPerView,DislikesPerView,
                            AdConsequentiam, AdHomien, AdPopulum, FalseCause, 
                            Polarisation, InvokingEmotion, Conspiracy, Trolling, DeflectingBlame,
                            MisrepresentationScripture, CherryPickedData)) 
temp1$LikestoDislikes <- irad$Likes/irad$Dislikes
temp1$LikestoDislikes[temp1$LikestoDislikes==Inf] <- NA
temp1$sumallrhetoric <- temp1 %>% select(AdConsequentiam:CherryPickedData) %>% apply(.,1,sum)

iradmainvars <- data.frame(temp1,
                           temp1 %>% select(c(MisinformationPerMinute, BetweennessCentrality, Views,
                                              VideoLength, LikestoDislikes ,LikesPerView, DislikesPerView, sumallrhetoric)) %>% 
                                     mutate_all(~ log(. + .0001)) %>%
                                     rename_all( ~paste0(., "_log") ))
multi.hist(iradmainvars%>%select(contains("log")))


#corrplot...
RM  <- cor(iradmainvars%>%select(contains("log")))
RM2 <- cor.mtest(iradmainvars%>%select(contains("log")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)
#dev.print(pdf,paste(figdir,"cormat.pdf",sep="/"))


```
## Predict various outcomes for Radical Islamist

### Predict views for Radical Islamist
```{r regradviews, echo=TRUE, warning=FALSE, message=FALSE}

radindepvars <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log: LikestoDislikes_log,sumallrhetoric_log)) %>% select(-Views_log)),collapse=" + ")

allradregFormula <- as.formula(paste("Views_log ~ ",radindepvars))
viewmod <- lm(allradregFormula, data=iradmainvars, na.action=na.omit)
allradregs <- ols_step_all_possible(viewmod)
plot(allradregs)

topmodels <- allradregs[order(allradregs$n,-allradregs$rsquare) , ]
topmodels[!duplicated(topmodels$n),]

#summarize the 'best' model 
radindepvars2 <- paste(unlist(str_split(allradregs[6,]$predictors," ")),collapse=" + ")
radbmFormula <- as.formula(paste("Views_log ~ ", radindepvars2))
viewbestmod <- lm(radbmFormula, data=iradmainvars)
summary(viewbestmod)

```

### Predict centrality for Radical Islamist
```{r regradcent, echo=TRUE, warning=FALSE, message=FALSE}

radindepvars3 <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-BetweennessCentrality_log)),collapse=" + ")

allradregFormula2 <- as.formula(paste("BetweennessCentrality_log ~ ",radindepvars3))
centmod <- lm(allradregFormula2, data=iradmainvars)
allradregs2 <- ols_step_all_possible(centmod)
plot(allradregs2)

topmodels2 <- allradregs2[order(allradregs2$n,-allradregs2$rsquare) , ]
topmodels2[!duplicated(topmodels2$n),]

#summarize the 'best' model
radindepvars4 <- paste(unlist(str_split(allradregs2[8,]$predictors," ")),collapse=" + ")
radbmFormula2 <- as.formula(paste("BetweennessCentrality_log ~ ", radindepvars4))
centbestmod <- lm(radbmFormula2, data=iradmainvars)
summary(centbestmod)

```

### Predict likes to dislikes for Radical Islamist
```{r regradl2d, echo=TRUE, warning=FALSE, message=FALSE}

radindepvars5 <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log:VideoLength_log,sumallrhetoric_log))),collapse=" + ")

allradregFormula3 <- as.formula(paste("LikestoDislikes_log ~ ",radindepvars5))
radl2dmod <- lm(allradregFormula3, data=iradmainvars)
allradregs3 <- ols_step_all_possible(radl2dmod)
plot(allradregs3)

topmodels3 <- allradregs3[order(allradregs3$n,-allradregs3$rsquare) , ]
topmodels3[!duplicated(topmodels3$n),]

#summarize the 'best' model
radindepvars6 <- paste(unlist(str_split(allradregs3[1,]$predictors," ")),collapse=" + ")
radbmFormula3 <- as.formula(paste("LikestoDislikes_log ~ ", radindepvars6))
l2dbestmod <- lm(radbmFormula3, data=iradmainvars)
summary(l2dbestmod)

```

## Compare radicalism to Islamophobia
```{r compr2p, echo=TRUE, warning=FALSE, message=FALSE}
#plot violins side by side
plotvn <- c("Misinfo/Min", "Centrality",   "Views"    , "VidLength",  "Like2Dislike",   "Likes/View",  "Dislikes/View", "SumRhetoric" )
x11(width=20,height=10)
vioplot(iphomainvars %>% select(contains("_log")), col = "brown", plotCentre = "line", side = "right",las=1,names=plotvn)
vioplot(iradmainvars %>% select(contains("_log")), col = "darkgreen", plotCentre = "line", side = "left", add = T)
title(xlab="Variable",ylab="Measure (log transformed)")
legend(7,12, fill = c("brown", "darkgreen"), legend = c("Islamophobic", "Islamist"), title = "Type of video")

#combined data set in case statistics are wanted
phorad <- bind_rows(iphob,irad,.id="radorphob")



```


