---
title: "youtube"
author: "StephanLewandowsky"
date: "2019-12-31"
output: 
   workflowr::wflow_html:
     code_folding: hide
     number_sections: yes
     toc: yes
     toc_depth: 3
     toc_float: yes
     theme: cosmo
     highlight: textmate
editor_options:
  chunk_output_type: console
---

## Introduction

```{r echo=TRUE, warning=FALSE, message=FALSE, results="hide"}
rm(list=ls())
library(lattice)
library(ggplot2)
library(tabplot)
library(tidyverse)
library(lme4)
library(RColorBrewer)
library(gridExtra)
library(stringr)
library(Hmisc)
library(reshape2)
library(psych)
library(scales)
library(summarytools) #contains descr()
library(foreign) #for SPSS
library(workflowr)
library(olsrr)
library(corrplot)
library(vioplot)

#define working directories and get functions ready
inputdir <- "data"
source ("analysis/youtubefuncs.R")

iphob <- read.spss(paste(inputdir,"IslamophobiaSPSSDATA.sav",sep="/"), use.value.labels = TRUE, to.data.frame = TRUE)
irad <-  read.spss(paste(inputdir,"RadicalisationSPSS.sav",sep="/"), use.value.labels = TRUE, to.data.frame = TRUE)
irad <- irad[!rowSums(is.na(irad))==dim(irad)[2], ]
```

## Summary statistics for Islamophobia
```{r summary, echo=TRUE, warning=FALSE, message=FALSE}
descr(iphob)
tableplot(iphob)

temp1 <- iphob %>% select(c(Modularity,MisinformationPerMinute,BetweennessCentrality,
                            Views,VideoLength,LikestoDislikes,LikesPerView,DislikesPerView,
                            AdConsequentiam, AdHomien, AdPopulum, FalseCause, HastyGeneralisations,
                            Polarisation, InvokingEmotion, Conspiracy, Trolling, DeflectingBlame,
                            MisrepresentationScripture, CherryPickedData)) 
#zero likes is a clear outlier after log transform, so remove it
temp1$LikesPerView[temp1$LikesPerView==0]<-NA
temp1$LikestoDislikes[temp1$LikestoDislikes==0]<-NA
temp1$sumallrhetoric <- temp1 %>% select(AdConsequentiam:CherryPickedData) %>% apply(.,1,sum)

#now look at detailed endogenous variables
temp2 <- iphob %>% select(AdConsequentiam:MisrepresentationScripture) %>% rename_all( ~paste0(., "_det") )

iphomainvars <- data.frame(temp1,
                           temp1 %>% select(c(MisinformationPerMinute, BetweennessCentrality, Views,
                                              VideoLength, LikestoDislikes ,LikesPerView, DislikesPerView, sumallrhetoric)) %>% 
                                     mutate_all(~ log(. + .0001)) %>%
                                     rename_all( ~paste0(., "_log") ),
                           temp2)
multi.hist(iphomainvars%>%select(contains("log")))


#corrplot...
RM  <- cor(iphomainvars%>%select(contains("log")))
RM2 <- cor.mtest(iphomainvars%>%select(contains("log")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
#colnames(RM) <- rownames(RM) <- c("Conservatism","Truth Knowable","Intuitive","Conspiracism","Need for Chaos","Knowledge Source",
#"Consensus AIDS","Consensus Vaccinations","Consensus Climate")
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)
#dev.print(pdf,paste(figdir,"cormat.pdf",sep="/"))
RM  <- cor(iphomainvars%>%select(contains("det")))
RM2 <- cor.mtest(iphomainvars%>%select(contains("det")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
#colnames(RM) <- rownames(RM) <- c("Conservatism","Truth Knowable","Intuitive","Conspiracism","Need for Chaos","Knowledge Source",
#"Consensus AIDS","Consensus Vaccinations","Consensus Climate")
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)

```
## Predict various outcomes for Islamophobia

### Predict views for Islamophobia, first from exogenous then endogenous parameters
```{r regphobviews, echo=TRUE, warning=FALSE, message=FALSE}

dv <- "Views_log"
exovars1 <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-dv)),collapse=" + ")
do1reg(dv, exovars1, iphomainvars)   
   
endovars4all <- paste(names(iphomainvars %>% select(contains("det"))),collapse=" + ")
do1reg(dv, endovars4all, iphomainvars)   

```

### Predict centrality for Islamophobia, first from exogenous then endogenous parameters
```{r regphobcent, echo=TRUE, warning=FALSE, message=FALSE}

dv2 <- "BetweennessCentrality_log"
exovars2 <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-dv2)),collapse=" + ")
do1reg(dv2, exovars2, iphomainvars)   
do1reg(dv2, endovars4all, iphomainvars)   

```

### Predict likes to dislikes for Islamophobia, first from exogenous then endogenous parameters
```{r regphobl2d, echo=TRUE, warning=FALSE, message=FALSE}

dv3 <- "LikestoDislikes_log"
#note that all like variables are removed from list of potential predictors
exovars3 <- paste(names(iphomainvars %>% select(c(MisinformationPerMinute_log:DislikesPerView_log,sumallrhetoric_log)) %>% select(-contains("ikes"))),collapse=" + ")
do1reg(dv3, exovars3, iphomainvars)  
do1reg(dv3, endovars4all, iphomainvars) 

```


## Summary statistics for Radical Islamist videos
```{r radsummary, echo=TRUE, warning=FALSE, message=FALSE}
descr(irad)
tableplot(irad)

radtemp1 <- irad %>% select(c(Modularity,MisinformationPerMinute,BetweennessCentrality,
                            Views,VideoLength,LikesPerView,DislikesPerView,
                            AdConsequentiam, AdHomien, AdPopulum, FalseCause, 
                            Polarisation, InvokingEmotion, Conspiracy, Trolling, DeflectingBlame,
                            MisrepresentationScripture, CherryPickedData)) 
radtemp1$LikestoDislikes <- irad$Likes/irad$Dislikes
radtemp1$LikestoDislikes[radtemp1$LikestoDislikes==Inf] <- NA
radtemp1$sumallrhetoric <- radtemp1 %>% select(AdConsequentiam:CherryPickedData) %>% apply(.,1,sum)

#now look at detailed endogenous variables, omitting those with no variance
radtemp2 <- irad %>% select(AdConsequentiam:MisrepresentationScripture) %>% 
                     rename_all( ~paste0(., "_det") ) %>% 
                     select(which(as.numeric(lapply(.,sd)) != 0))

iradmainvars <- data.frame(radtemp1,
                           radtemp1 %>% select(c(MisinformationPerMinute, BetweennessCentrality, Views,
                                              VideoLength, LikestoDislikes ,LikesPerView, DislikesPerView, sumallrhetoric)) %>% 
                                     mutate_all(~ log(. + .0001)) %>%
                                     rename_all( ~paste0(., "_log") ),
                           radtemp2)
multi.hist(iradmainvars%>%select(contains("log")))


#corrplot...
RM  <- cor(iradmainvars%>%select(contains("log")))
RM2 <- cor.mtest(iradmainvars%>%select(contains("log")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)
#dev.print(pdf,paste(figdir,"cormat.pdf",sep="/"))

RM  <- cor(iradmainvars%>%select(contains("det")))
RM2 <- cor.mtest(iradmainvars%>%select(contains("det")), conf.level = .95)
diag(RM)<-NA

x11(width=11,height=10)
corrplot.mixed(RM, lower.col = "black", number.cex = 1.2,insig = "blank",
                   upper="ellipse",p.mat = RM2$p,sig.level=.05,
                   tl.pos="lt",tl.col="black",na.label = ".",bg="lightgray",
                   tl.cex=1.5,tl.srt=60)

```
## Predict various outcomes for Radical Islamist

### Predict views for Radical Islamist, first from exogenous then endogenous parameters
```{r regradviews, echo=TRUE, warning=FALSE, message=FALSE}

raddv <- "Views_log"
radexovars1 <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log:sumallrhetoric_log)) %>% select(-raddv)),collapse=" + ")
do1reg(raddv, radexovars1, iradmainvars)   
   
radendovars4all <- paste(names(iradmainvars %>% select(contains("det"))),collapse=" + ")
do1reg(raddv, radendovars4all, iradmainvars)   

```

### Predict centrality for Radical Islamist, first from exogenous then endogenous parameters
```{r regradcent, echo=TRUE, warning=FALSE, message=FALSE}

raddv2 <- "BetweennessCentrality_log"
radexovars2 <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log:sumallrhetoric_log)) %>% select(-raddv2)),collapse=" + ")
do1reg(raddv2, radexovars2, iradmainvars)   
do1reg(raddv2, radendovars4all, iradmainvars)   

```

### Predict likes to dislikes for Radical Islamist, first from exogenous then endogenous parameters
```{r regradl2d, echo=TRUE, warning=FALSE, message=FALSE}

raddv3 <-  "LikestoDislikes_log"
#note that all like variables are excluded from list of potential predictors
radexovars3 <- paste(names(iradmainvars %>% select(c(MisinformationPerMinute_log:VideoLength_log,sumallrhetoric_log))),collapse=" + ")
do1reg(raddv3, radexovars3, iradmainvars)  
do1reg(raddv3, radendovars4all, iradmainvars)   

```

## Compare radicalism to Islamophobia
```{r compr2p, echo=TRUE, warning=FALSE, message=FALSE}
#plot violins side by side
plotvn <- c("Misinfo/Min", "Centrality",   "Views"    , "VidLength",  "Like2Dislike",   "Likes/View",  "Dislikes/View", "SumRhetoric" )
x11(width=20,height=10)
vioplot(iphomainvars %>% select(contains("_log")), col = "brown", plotCentre = "line", side = "right",las=1,names=plotvn)
vioplot(iradmainvars %>% select(contains("_log")), col = "darkgreen", plotCentre = "line", side = "left", add = T)
title(xlab="Variable",ylab="Measure (log transformed)")
legend(7,12, fill = c("brown", "darkgreen"), legend = c("Islamophobic", "Islamist"), title = "Type of video")

#combined data set in case statistics are wanted
phorad <- bind_rows(iphob,irad,.id="radorphob")


```


